Quantifying uncertainty in Pareto estimates of global lake area

### 2022-12-19 manuscript/figures.Rmd
fix color typo in fig caption

```{r fig.cap="Censored lake area edf (solid line) and transformed cdf estimate (dashed line) compared against the HydroLAKES dataset.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/predict_censor-1.pdf")
```

```{r fig.cap="Stan model code", echo=FALSE, fig.width=1,out.height="5in"}
knitr::include_graphics("../manuscript/figures/stan.pdf")
```

>>>>

```{r fig.cap="Simulated lake area (purple line) where the portion calculated from the edf (>= 0.1 $km^2$) is denoted by a solid line and the portion calculated from the transformed cdf (< 0.1 $km^2$) is denoted by a dashed line. For comparison, the edf of the HydroLAKES dataset (solid yellow line) is also shown.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/predict_censor-1.pdf")
```

### 2022-12-19 manuscript/manuscript.tex
fix color typo in fig caption

\begin{figure}
	\centering
	\includegraphics{figures/predict_censor-1}
	\caption{Simulated lake area (blue line) where the portion calculated from the edf (>= 0.1 $km^2$) is denoted by a solid line and the portion calculated from the transformed cdf (< 0.1 $km^2$) is denoted by a dashed line. For comparison, the edf of the HydroLAKES dataset (solid red line) is also shown.}
	\label{fig:predict_censor}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics{figures/predict_censor-1}
	\caption{Simulated lake area (purple line) where the portion calculated from the edf (>= 0.1 $km^2$) is denoted by a solid line and the portion calculated from the transformed cdf (< 0.1 $km^2$) is denoted by a dashed line. For comparison, the edf of the HydroLAKES dataset (solid yellow line) is also shown.}
	\label{fig:predict_censor}
\end{figure}
